Modeling Time-Variable Elemental Abundances in Coronal Loop Simulations

### 2024-06-08 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{amsmath}

@@

\section*{Acknowledgments}
At the time of writing, the implementation into \texttt{ebtel++} is publicly available as an unmerged pull request on GitHub: \url{https://github.com/rice-solar-physics/ebtelPlusPlus/pull/87}.  This paper is fully reproducible with the \texttt{showyourwork!} package, and can be downloaded from \url{https://github.com/jwreep/ebtel_abundances}.

>>>>

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{hyperref}

@@

\section*{Acknowledgments}
At the time of writing, the implementation into \texttt{ebtel++} is publicly available as an unmerged pull request on GitHub: \url{https://github.com/rice-solar-physics/ebtelPlusPlus/pull/87}.

This paper is fully reproducible with the \href{https://github.com/showyourwork/showyourwork}{\showyourwork} package, and can be downloaded from \url{https://github.com/jwreep/ebtel_abundances}.  This package strives for full reproducibility and transparency in science.  Each figure in this paper contains a hyperlink with the Github logo that points to the script used to generate the plots in that figure.  Additionally, the whole paper can be generated with a single command, including running the \texttt{ebtel++} simulations, reading in the data, and producing the figures.  Users can then additionally reconfigure the simulations, the plots, or the scripts to their own liking to validate or extend this research.
